Introduction to *cellcount* - Draft vignette

### 2024-03-14 cellcount_intro.Rmd
Updated - small changes to text

---
title: "Introduction to *cellcount* - Draft vignette"
author: 
  - name: Tyler E. Harman 
    affiliation: Consolidated Safety Services, Fairfax, VA 22031, USA
      National Oceanic and Atmospheric Administration, National Centers for Coastal Ocean Science, Beaufort, NC 28516, USA
    affiliation_email: tyler.harman@noaa.gov
    orcid_id: 0000-0001-5007-8170

@@

  - name: David E. Berthold
    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA

  - name: H. Dail Laughinghouse
    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA
    orcid_id: 0000-0003-1018-6948

  - name: Kaytee Pokrzywinski
    affiliation: National Oceanic and Atmospheric Administration, National Centers for Coastal Ocean Science, Beaufort, NC 28516, USA
    orcid_id: 0000-0003-1523-9930
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
```

@@

```{r}
images <- list.files("./inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
images <- list.files("./inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

savdir <- ("./inst/extdata/test_data/")
image_savdir <- ("./inst/extdata/test_results/")
images <- list.files("./inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("./inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

Informal discussions with researchers have expressed interest in an easy-to-use analysis interface for inexperienced R users
to utilize the ***cellcount*** package. The following overview uses 'Shiny' apps to enter input data and process images. This results in the use of two functions, *input_data_GUI* and *analyze images_GUI*, to run the entire analysis process as outlined previously, and in the **sandbox_analysis_test.R** script. Several packages are required to utilize these UI tools:

>>>>

---
title: "Introduction to *cellcount* - Draft vignette"
author: 
  - name: Tyler E. Harman 
    affiliation: Consolidated Safety Services (Contracted to NOAA NCCOS), Fairfax, VA 22031, USA
    affiliation_email: tyler.harman@noaa.gov
    orcid_id: 0000-0001-5007-8170

@@

  - name: Kaytee Pokrzywinski, PhD
    affiliation: National Oceanic and Atmospheric Administration, National Centers for Coastal Ocean Science, Beaufort, NC 28516, USA
    orcid_id: 0000-0003-1523-9930
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

```{r,message=FALSE}
savdir <- ("C:/file path for saving CSV data")
image_savdir <- ("C:/file path for saving converted images")
```
```{r,include=FALSE}
savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
```

@@

```{r}
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Microcystis_F192_40x/", pattern = "tif", full.name = F)
```

@@

savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/NZ_Anabena_60x/", pattern = "tif", full.name = F)

@@

savdir <- ("./cellcount_files_HABF/inst/extdata/test_data/")
image_savdir <- ("./cellcount_files_HABF/inst/extdata/test_results/")
images <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = T)
images_names <- list.files("./cellcount_files_HABF/inst/extdata/test_images/Shewanella_100x_DAPI/", pattern = "tif", full.name = F)

@@

Informal discussions with researchers have expressed interest in an easy-to-use analysis interface for inexperienced R users
to utilize the ***cellcount*** package. The following overview uses 'Shiny' apps to enter input data and process images. This results in the use of two functions, *input_data_GUI* and *analyze images_GUI*, to run the entire analysis process as outlined previously, and in the **cellcount_sandbox.R** script under the
<span style="text-decoration:underline">*cellcount_files_HABF*</span> folder. Several packages are required to utilize these UI tools:
